---
title: "Atividade - Aula 10 - 17 11 23"
format: 
  html:
    embed-resources: true
editor: 
  markdown: 
    wrap: 72
---

# Exercise 1 - Linear Model

### 1 - Using package BatchGetSymbols, download adjusted price data for \^BVSP and GRND3.SA from 2015 to 2023.

```{r}
library(yfR)
library(tidyverse)

ibov <- yf_get('^BVSP', 
               first_date = '2015-01-01',
               last_date = '2023-11-16',
               be_quiet = T)

ibov <-  ibov |> 
  select(ref_date, ret_adjusted_prices) |> 
  rename(ret_adjusted_ibov = ret_adjusted_prices)

grnd3 <- yf_get('GRND3.SA', 
                first_date = '2015-01-01',
                last_date = '2023-11-16',
                be_quiet = T)

grnd3 <- grnd3 |> 
  select(ref_date, ret_adjusted_prices) |> 
  rename(ret_adjusted_grnd3 = ret_adjusted_prices)

base_modelo <- left_join(grnd3, ibov, by = "ref_date")

base_modelo$ret_adjusted_ibov |> summary()

base_modelo <- base_modelo |> 
  filter(!is.na(ret_adjusted_ibov))

base_modelo$ret_adjusted_grnd3 |> summary()
```

### 2 - Estimate the beta of GRND3 from the following model:

Rt = α + βRM,t + ϵt

```{r}

modelo1 <- lm(ret_adjusted_grnd3 ~
                ret_adjusted_ibov,
              data = base_modelo)

summary(modelo1)
```

### 3 - Estimate a new market model with a dummy for negative returns:

Rt = α + β1RM,t + β2DtRM,t + ϵt

Where Dt=1 if RM,t\<0 and DT=0 otherwise

```{r}
base_modelo <- base_modelo |> 
  mutate(Dnr = if_else(ret_adjusted_ibov < 0, 1, 0))

modelo2 <- lm(ret_adjusted_grnd3 ~
                ret_adjusted_ibov + Dnr,
              data = base_modelo)

summary(modelo2)
```

#### 4 - With the first model (without dummies), use package car to test the hipothesis that α=0 and β=1

```{r}
library(car)

intercept <- 0
beta <- 1

test_matrix <- matrix(c(modelo1$coefficients[1],  
                        modelo1$coefficients[2]))  

# hypothesis matrix 
hyp_mat <- matrix(c(1,0,
                    0,1),nrow = 2)

# do test
my_waldtest <- linearHypothesis(
  modelo1,
  hypothesis.matrix = hyp_mat, 
  rhs = test_matrix)

# print result
print(my_waldtest)
```

### 5 - Test the underlying assumptions of the previous linear model with package gvlma

```{r}
library(gvlma)

gvmodelo1 <- gvlma(modelo1) 

summary(gvmodelo1)
```

# Exercise 2 - Linear Models

### 1 - Using package BatchGetSymbols, download adjusted price data for PETR3, PETR4, GGBR3, GGBR4 from 2010 to 2018.

```{r}
acoes <- c('PETR3.SA', 'PETR4.SA', 'GGBR3.SA', 'GGBR4.SA')

df <- yf_get(acoes,
             first_date = '2010-01-01',
             last_date = '2018-12-31', 
             be_quiet = T)

ibov <- yf_get('^BVSP', 
               first_date = '2010-01-01',
               last_date = '2018-12-31', 
               be_quiet = T)

ibov <-  ibov |> 
  select(ref_date, ret_adjusted_prices) |> 
  rename(ret_adjusted_ibov = ret_adjusted_prices)

base_modelo2 <- left_join(df, ibov, by = "ref_date")

base_modelo2$ret_adjusted_ibov |> summary()

base_modelo2 <- base_modelo2 |> 
  filter(!is.na(ret_adjusted_ibov))

base_modelo2$ret_adjusted_prices |> summary()
```

### 2 - Using loops, estimate and save the beta of all stocks in a dataframe with two columns (ticker, beta):

Rt = α + βRM,t + ϵt

```{r}

betas <- data.frame(ticker = character(0),
                    beta = numeric(0))

resultado_modelos <- list()

for (acao_atual in acoes){
  
  base_atual <- base_modelo2 |> 
    filter(ticker == acao_atual)
  
  modelo_atual <- lm(ret_adjusted_prices ~
                       ret_adjusted_ibov,
                     data = base_atual)
  
  resultado_modelos[[length(resultado_modelos)+1]] <-  modelo_atual
  
  betas <- bind_rows(
    betas, 
    data.frame(ticker = acao_atual,
               beta = modelo_atual$coefficients[2]))
}

rownames(betas) <- NULL
betas
```

### 3 - Report the results of all models with texreg::screenreg in a single table

```{r}
library(texreg)

texreg::screenreg(l = resultado_modelos)
```
